Testing d3

### 2024-07-06 text/21/venn-diagram.Rmd
Updated rmd files

---
title: "Test diagrams"
author: "Steve Simon"
source: new
date: "2021-10-30"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

>>>>

---
title: "Test diagrams"
author: "Steve Simon"
source: new
date: "2021-10-30"
categories:
- Blog post
tags:
- Graphical display
- Rmarkdown graphs
output: html_document
page_update: complete
---

### 2024-07-06 text/21/very-simple-splines.Rmd
Updated rmd files

---
title: "Very simple spline models"
author: "Steve Simon"
date: "2021-10-29"
categories:
- Recommendation
tags:
- Linear regression
output: html_document
---

>>>>

---
title: "Very simple spline models"
source: new
author: "Steve Simon"
date: "2021-10-29"
categories:
- Recommendation
tags:
- Linear regression
- Rmarkdown graphs
output: html_document
page_update: complete
---

### 2024-07-06 text/21/zero-inflated-poisson.Rmd
Updated rmd files

---
title: "Zero-inflated models"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Zero-inflated models"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
- Rmarkdown graphs
output: html_document
page_update: complete
---

### 2024-07-06 text/22/testing-d3.Rmd
Updated rmd files

---
title: "Testing d3"
author: "Steve Simon"
date: "2022-06-01"
source: new
categories: 
- Blog post
tags: 
- Graphical display
output: html_document
---

@@

```{r setup}
library(r2d3)
```

@@

```{d3, data=runif(30), options=list(color='steelblue')}
svg.selectAll('rect')
  .data(data)
  .enter()
    .append('rect')
      .attr('width', function(d) { return d * 672; })
      .attr('height', '10px')
      .attr('y', function(d, i) { return i * 16; })
      .attr('fill', options.color);
```

>>>>

---
title: "Testing d3"
author: "Steve Simon"
date: "2022-06-01"
source: new
categories:
- Blog post
tags:
- Graphical display
- Rmarkdown graphs
output: html_document
page_update: complete
---

@@

```{r testing-d3-01}
library(r2d3)
```

@@

```{d3 testing-d3-02, data=runif(30), options=list(color='steelblue')}
svg.selectAll('rect')
  .data(data)
  .enter()
    .append('rect')
      .attr('width', function(d) { return d * 672; })
      .attr('height', '10px')
      .attr('y', function(d, i) { return i * 16; })
      .attr('fill', options.color);
```
